---
title: "mkdocs_workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mkdocs_workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```

```{r setup}
library(docmaker)
```

## Allow GitHUb pages in your repository


## mkdocs set-up and workflow

 - To build the site:

```{bash}
mkdocs build
```

 - To push the site

```{bash}
mkdocs gh-deploy --strict --force
```

## GitHub pages

To allow your repository to be build as a static web page, you can follow the
instructions from [github pages](https://pages.github.com/)

## Setting your repo with mkdocs

Once you clone your repository, go to your directory and in the terminal use
the following command, tha it will create all the initial documents:

```{bash}
$mkdocs new .
```

All the documentation about mkdocs is [here](https://www.mkdocs.org/)


After you have your repository set up, you can serve the site with:

```{bash}
$mkdocs serve
```


This will create all the static web page files and deploy locally the site. You
can check your served site on: `http://127.0.0.1:8000/`

### Using material theme

If you don't like the default theme for your static web page, you can use many
other themes. Here I used the material theme. All documentation can be found
[here](https://squidfunk.github.io/mkdocs-material/creating-your-site/)


To install the theme:

```{bash}
pip install mkdocs-material
```


Then, on your project `yml` file, you need to include the following:

```
theme:
  name: material
```

## Deploying your site

Now we are set. After you have your files ready, you need to send everything 
to github:

```{bash}
$mkdocs gh-deploy
```

We should see a message like this one:

```
INFO     -  Your documentation should shortly be available at: https://ronnyhdez.github.io/draweR/
```

# Don't control version your site folder!

Don't forget to put on your `.gitignore` file the `site` folder




