---
title: "mkdocs_workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mkdocs_workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```

```{r setup}
library(docmaker)
```

## Allow GitHUb pages in your repository


### Getting MkDocs

For this, I followed the instructions over [here](https://www.mkdocs.org/user-guide/installation/).
I got already python on my machine and I'm a Linux user, so I'm using 
Ubuntu 20.04

Given that I had already python I just installed MkDocs:

```{bash}
pip install mkdocs
```

Then I validated that the installation was succesful:

```{bash}
$ mkdocs --version
mkdocs, version 1.2.2 from /home/your_username/.local/lib/python3.8/site-packages/mkdocs (Python 3.8)
```

Done! I got MkDocs on my computer.

### Getting Matherial theme

I don't like the default theme that comes with MkDocs, so I changed to 
[Matherial](https://squidfunk.github.io/mkdocs-material/getting-started/).

To install this theme, you will need to run in the terminal:

```{bash}
$ pip3 install mkdocs-material
```

## Working on your notes

Now we are all set. We can start creating our Rmarkdown documents:

Create as many `Rmd` documents as you need. Each document will be a "section"
on your final website. 

Each of the titles and subtitles in your document will be sections inside the
specific page.

Also, use relative paths. This will make everything less error prone. 

Now, because we are going to use the package [docmaker](https://github.com/ronnyhdez/docmaker)
we need to follow a structure:

 - All your `Rmd` files should be in the root of your project.
 - Your data, images, pdfs files can be saved inside folders.
 - **Don't use `docs` folder**. This is a special folder designated to save the
 files needed to build the web page. `docmaker` package will be in charge of 
 the use of this folder, so you don't have to worry about it.
 
## Deploy and publish your notes with `docmaker`

So far, we have our notes. But we are still lacking the part of publishing in
our web page the notes. There are several steps to do this manually but after
many times repeating everything I decided to create a small R package to
automatize this steps. This package is called [dockmaer](https://github.com/ronnyhdez/docmaker)

You can install the package with:

```{r, eval = FALSE}
devtools::install_github("ronnyhdez/docmaker")
```

Now, on your console you can load the package:

```{r, eval = FALSE}
library(docmaker)
```

### Configure repo with `docmaker`

Before building and deploying our notes, we need to do some configuration steps
in our repository. `docmaker` can take care of this with the function:

```{r, eval = FALSE}
build_repo(github_page_url = "https://ronnyhdez.github.io/test_docmaker/",
           site_author = "Ronny A. Hernández Mora")
```

We can get the URL of our repository in the settings > page on GitHub. After
we enabled this in a step before, there should appear the URL designated by
GitHub for our web site.

The `site_author` should be our name.

This function will do the following:

 - Create a `yml` file
 - Add to the `.gitignore` the `site` folder
 - Create a `docs` folder

### Build and deploy notes

Because this is our first time, all of our notes (three in the example) are not
existing as `md` documents nor even built or deploy with mkdocs.

`docmaker` have a function to take **all the .Rmd files** existing in our project
root and do all the steps needed to deploy this ones:

```{r, eval = FALSE}
make_all_docs(deploy = TRUE)
```

This function will do the following:

 - Render all our `Rmd` files to `md`
 - Move the outputs (including images) to the `docs` folder
 - If we are using a `README.Rmd` file **this will be ignore**
 - Build the mkdocs
 - If `deploy` is set to `TRUE` it will deploy the notes.
 - Create an specifi branch for the pages deployment: `gh-deploy`
 
Now, given that we are using a new branch to be deployed, we need to go back to
GitHub pages and make a small change: change the branch selected to be build 
from `main` to `gh-pages`

After some seconds (or a few minutes), we should be able to see our site alive!

## More detailed steps

I have created a blog post with more detailed steps if you get confused with
the steps setting on your GitHub pages in [here](https://ronnyhdez.github.io/blog/posts/2021-12-11-usingmkdocsrmd/)

